---
title: "Exploratory Data Analysis"
author: "Dennis Irorere"
date: "July 27, 2018"
output:
  word_document: default
  pdf_document: default
---

Lesson 3
=================================================

## Reading in Data
The file have 99003 rows and 15 columns which represent a data of 99000 users of facebook and their information such as age, date of birth e.t.c
```{r}
getwd()
list.files()
pf <- read.csv("C://Users/Dennis/Downloads/pseudo_facebook.tsv", sep = "\t")
names(pf)
colnames(pf)
```

Our goal is to understand users behaviour and demographics, we want to understand what they are doing on facebook and what they use.

##Histogram of user's Birthdays
```{r}
library(ggplot2)
attach(pf)
qplot(x = dob_day, data = pf) + 
  scale_x_continuous(breaks = 1:31) + 
  facet_wrap(~dob_month, ncol = 3)
```


##Friend Count
```{r}
qplot(x = friend_count, data = pf)
```
How is this plot similar to Moira's first plot?

##Limiting axes
```{r}
qplot(x = friend_count, data = pf, xlim = c(0,1000))

qplot(x = friend_count, data = pf) + 
  scale_x_continuous(limits = c(0,1000))
```
## Adjusting the Bin Width
```{r}
qplot(x=friend_count, data = pf, binwidth = 25) +
  scale_x_continuous(limits = c(0,1000), breaks = seq(0,1000, 50))+
  facet_wrap(~gender)
```
#Omitting NA Gender observation
```{r}
qplot(x = friend_count, data = subset(pf, !is.na(gender)), binwidth = 10) +
  scale_x_continuous(limits = c(0,1000), breaks = seq(0,1000,50)) + 
  facet_wrap(~gender)
```
#Statistics by gender
```{r}
table(pf$gender)
by(pf$friend_count,pf$gender,summary)
```
#Tenure
```{r}
qplot(x = tenure, data = pf, binwidth = 30, 
      color = I('black'), fill = I('#099DD9'))
```
##Tenure years, instead of days
```{r}
qplot(x = tenure / 365, data = pf, binwidth = .25,
      xlab = "Number of years using Facebook",
      ylab = "Number of users in sample",
      color = I('black'), fill = I('#099DD9')) +
  scale_x_continuous(breaks = seq(1,7,1), limits = c(0,7))
```
##Users Age
```{r}
qplot(x = age, data = pf, binwidth = 1,
      color = I('black'), fill = I('#5760AB')) + 
  scale_x_continuous(breaks = seq(0,113,5))

```
#Transforming Data
```{r}
qplot(x = friend_count, data = pf)
summary(pf$friend_count)
summary(log10(pf$friend_count + 1))
summary(sqrt(pf$friend_count))
```

##Plotting histogram with transform data
```{r}
qplot(x = log10(pf$friend_count + 1), data = pf, binwidth = 0.25)
library(gridExtra)

p1 <- qplot(x = friend_count, data = pf)
p2 <- qplot(x = log10(pf$friend_count + 1), data = pf)
p3 <- qplot(x = sqrt(friend_count), data = pf)

grid.arrange(p1,p2,p3, ncol = 1)
```

## Transforming Data Alternate Solution
## Use scales
```{r}
p1 <- ggplot(aes(x = friend_count), data = pf) + geom_histogram()
p2 <- p1 + scale_x_log10()
p3 <- p1 + scale_x_sqrt()

grid.arrange(p1,p2,p3, ncol = 1)
```
##Adding a Scaling layer
```{r}
logScale <- qplot(x = log10(friend_count), data = pf)

countscale <- ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram() + 
  scale_x_log10()

grid.arrange(logScale, countscale, ncol = 2)
```
#Lesson 4 two variable
You will learn how to visualize two variables and quantify the relationship. By the use of data aggregation, conditional means and scatter plots. 
##Noisy scatterplots
```{r}
library(ggplot2)
library(dplyr)
cor.test()
```
```{r}
names(pf)
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_jitter(alpha = 1/20)
```
Using the ggplot to plot two variable data types
```{r}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point() + xlim(13, 90)

summary(age, pf)
```
##Ggplot syntax
```{r}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point(alpha = 1/20)
```
##Over plotting
```{r}
ggplot(aes(age, friend_count), data = pf) + 
  geom_jitter(alpha = 1/20) +  
```








































































































































































































































































